Title Goes Here

### 2020-04-17 analysis/paper/paper.Rmd
GM

# Let's save the output for each one
saveRDS(CAA18_tm, here::here("analysis/data/derived-data/CAA18_topic_model.rds"))
saveRDS(EAA18_tm, here::here("analysis/data/derived-data/EAA18_topic_model.rds"))
saveRDS(SAA18_tm, here::here("analysis/data/derived-data/SAA18_topic_model.rds"))
```

>>>>

# Let's save the output for each one
saveRDS(CAA18_tm, here::here("analysis/data/derived-data/CAA18_topic_model.rds"))
saveRDS(EAA18_tm, here::here("analysis/data/derived-data/EAA18_topic_model.rds"))
saveRDS(SAA18_tm, here::here("analysis/data/derived-data/SAA18_topic_model.rds"))

# gender model
CAA18_gm <- get_the_gender_data(CAA18)
saveRDS(CAA18_gm, here::here("analysis/data/derived-data/CAA18_gender_model.rds"))
SAA18_gm <- get_the_gender_data(SAA18)
saveRDS(SAA18_gm, here::here("analysis/data/derived-data/SAA18_gender_model.rds"))
```
